---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Michael Sewerin"
date: "28 November 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This is the documentation for the Course Project 'Shiny Application and Reproducible Pitch' of the Coursera course 'Developing Data Products' which is a part of the Data Science Specialization.

The task was to build a shiny application which should include the following:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in server.R
3. Some reactive output displayed as a result of server calculations


## About the application

I wrote a simple application that takes a value in degree Celsius as input and calcuates the Fahrenheit value for it and prints it. Using the slider the user can select the value in Celsius.

The application is running on:
https://misewerin.shinyapps.io/Shiny_App/

The code can be found in my github repository:
https://github.com/misewerin/shiny/

## Formula

The formula I used to do the calculation is the following:

```{r eval = FALSE}
fahrenheitValue <- celsiusValue * 9/5 + 32
```

## Slide with example results

```{r}
celsiusValue <- 25
fahrenheitValue <- celsiusValue * 9/5 + 32
fahrenheitValue
```

```{r}
celsiusValue <- 0
fahrenheitValue <- celsiusValue * 9/5 + 32
fahrenheitValue
```

```{r}
celsiusValue <- 15
fahrenheitValue <- celsiusValue * 9/5 + 32
fahrenheitValue
```

